\chapter{Project Focus}
This report is centered about Parental Control (PC) in Smart Home (SH). This chapter will explain what PC and SH is, as well as explorer a field of different possibilities and narrow the possibilities down to a reasonable amount of goals for this project.

%What is smart home
\section{Smart Home}
A Smart Home can refer to multiple forms of improvement on a home. Most commonly is home automation, environment friendly improvements and power saving improvements. In this report we will only regard Smart Home in relation to home automation, however environment friendly- and power saving improvements, sometimes also springs out of home automation. For example if you automate the washing machine to start at a certain hour of the day, it will both be convenient as well as power saving.\\
\\
But a Smart Home, can be much more. Different examples of implementable features is as follows:

\begin{itemize}
	\item Automated security
	\item Music systems
	\item Theater systems
	\item Voice commands
	\item Automatic ordering of groceries
	\item Delayed start on an oven
	\item Automated coffee machines
	\item Light control
	\item Power control on leaving home
	\item And much more
\end{itemize}

This report is about a less common feature of a Smart Home. It is about Parental Control, a concept explained in \ref{parentalControl}.

%What is parental control
\section{Parental Control}
\label{parentalControl}
Parental Control (PC) is a concept most people know from their TV at home or computers. A concept used mainly by parents to protect their children from fx. internet sites with adult content or TV channels of the same kind.\\
But in a Smart Home, this concept could be taken even further. Many electronic devises does not implement a PC feature, and some of those which does, does not allow to block all content.\\
We want to create a system that could help parents manage their children's time
%Write about the brainstorm we did
%Narrow down the area we want to covor
%Specify what must be done, in order for it to succed